\documentclass[a4paper,12pt]{article}
\usepackage{graphicx}
\usepackage{fixltx2e}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{url}
\lstset {
tabsize=2
}
\pagestyle{myheadings}
\graphicspath { {'/'} }
\begin{document}
	\author{Quang - Vinh DANG \\ COAST team, Inria Nancy}
	\title{Technical Report\\ Evaluating delays faced by users in large scale settings using GoogleDocs and MUTE}\maketitle

\section{Measurement}

\cite{R1, R2, R3, R6} measures:
\begin{itemize}
	\item How much A \footnote{A: sender, B: receiver} send, what is payoff of A
	\item How much B send back, what is the proportion, what is payoff of B
\end{itemize}

They calculate mean and standard deviation for each value then compare.

\cite{R4} measures the percentage of reward between users.

\cite {R5}, which is very close, measure the proportion of sending and sending back, average earning and hazard percentage (i.e, the receiver "betrays" the sender)
\begin{thebibliography}{99}

\bibitem{R1} Ben-Ner, Avner, and Louis Putterman. "Trust, communication and contracts: An experiment." Journal of Economic Behavior \& Organization 70, no. 1 (2009): 106-121.

\bibitem{R2} Burks, Stephen V., Jeffrey P. Carpenter, and Eric Verhoogen. "Playing both roles in the trust game." Journal of Economic Behavior \& Organization 51, no. 2 (2003): 195-216.

\bibitem{R3} Cox, James C. "How to identify trust and reciprocity." Games and economic behavior 46, no. 2 (2004): 260-281.

\bibitem{R4} Anderhub, Vital, Dirk Engelmann, and Werner Güth. "An experimental study of the repeated trust game with incomplete information." Journal of Economic Behavior \& Organization 48, no. 2 (2002): 197-216. 

\bibitem{R5} Engle-Warnick, Jim, and Robert L. Slonim. "The evolution of strategies in a repeated trust game." Journal of Economic Behavior \& Organization 55, no. 4 (2004): 553-573.

\bibitem{R6} Dubois, Dimitri, Marc Willinger, and Thierry Blayac. "Does players’ identification affect trust and reciprocity in the lab?." Journal of Economic Psychology 33, no. 1 (2012): 303-317.
\end{thebibliography}	
\end{document}