---
title: "Report on issues of AAMAS"
author: "Vinh Dang"
date: "25 January 2016"
output: pdf_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=8, fig.path='all_data/',
                      warning=FALSE, message=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=50))
```

```{r echo=FALSE}
source("ProcessData.R")
```

# Issues of AAMAS

## Showing that there is fluctuating behaviors in games


```{r echo=FALSE}

#to store average sending and standard deviation of sending of all players from 3 datasets
all_avg = c()
all_std = c()
```

```{r echo=FALSE}
zTT <- readMultiXLS ("./all_data")
  zTT[2]$subjects$my_send_proportional <- ifelse(zTT[2]$subjects$Type == 0, zTT[2]$subjects$Contribution/10, ifelse(zTT[2]$subjects$PartnerDecision > 0, zTT[2]$subjects$Contribution/3/zTT[2]$subjects$PartnerDecision, -1))
  
  zTT[2]$subjects$CurrGameProfit <- ifelse(zTT[2]$subjects$Type == 0, zTT[2]$subjects$PartnerDecision - zTT[2]$subjects$Contribution, zTT[2]$subjects$PartnerDecision*3 - zTT[2]$subjects$Contribution)
  # Numbers of user of a group
  num_users = 6
  # Number of rounds each user play to each other
  average_rounds = 5
  # Number of games for each group 
  num_games = 4
  # Number of rounds for each game (should be 25)
  num_rounds_per_game = (num_users - 1) * average_rounds 
  # Number of rounds for each experiment (should be 100, because we have 4 games)
  num_rounds_per_exp = num_rounds_per_game * num_games
  # Number of experiments (it is 5 at the time of writing, 
  # but can be increased if we organize more experiments)
  num_exp = nrow (zTT[1]$globals) / num_rounds_per_exp
  
  Type_names = c("SENDER", "RECEIVER")
  SIMPLE_GAME_ORDERS =      c(3,2,4,1,2)
  ID_GAME_ORDERS =          c(1,4,1,2,3)
  SCORE_GAME_ORDERS =       c(2,1,3,4,4)
  COMBINE_GAME_ORDERS =     c(4,3,2,3,1)
  
  # first, create empty data frames to hold all the particular games
  simple_games <- zTT[2]$subjects[0,]
  id_games <- zTT[2]$subjects[0,]
  score_games <- zTT[2]$subjects[0,]
  combine_games <- zTT[2]$subjects[0,]
  
  for (exp_id in 1:num_exp) {
    first_round_of_exp_globals = (exp_id - 1) * num_rounds_per_exp + 1
    last_round_of_exp_globals = exp_id * num_rounds_per_exp
    globals_of_exp = zTT[1]$globals[first_round_of_exp_globals:last_round_of_exp_globals,]
    
    first_round_of_exp_subjects = (exp_id - 1) * num_rounds_per_exp * num_users + 1
    last_round_of_exp_subjects = exp_id * num_rounds_per_exp * num_users
    subjects_of_exp = zTT[2]$subjects[first_round_of_exp_subjects:last_round_of_exp_subjects,]
    
    SIMPLE_GAME_ORDER = globals_of_exp[1,]$SIMPLE_GAME
    ID_GAME_ORDER = globals_of_exp[1,]$ID_GAME
    SCORE_GAME_ORDER = globals_of_exp[1,]$SCORE_GAME
    COMBINE_GAME_ORDER = globals_of_exp[1,]$COMBINE_GAME
    
    simple_games <- rbind(simple_games, subjects_of_exp[((SIMPLE_GAME_ORDER - 1) * 
                                                           num_rounds_per_game * num_users + 1): 
                                                          (SIMPLE_GAME_ORDER * num_rounds_per_game * num_users),])
    id_games <- rbind(id_games, subjects_of_exp[((ID_GAME_ORDER - 1) * 
                                                   num_rounds_per_game * num_users + 1): 
                                                  (ID_GAME_ORDER * num_rounds_per_game * num_users),])
    score_games <- rbind(score_games, subjects_of_exp[((SCORE_GAME_ORDER - 1) * 
                                                         num_rounds_per_game * num_users + 1): 
                                                        (SCORE_GAME_ORDER * num_rounds_per_game * num_users),])
    combine_games <- rbind(combine_games, subjects_of_exp[((COMBINE_GAME_ORDER - 1) * 
                                                             num_rounds_per_game * num_users + 1): 
                                                            (COMBINE_GAME_ORDER * num_rounds_per_game * num_users),])
  }
  
  # data of senders in simple games
  s = simple_games[simple_games$Type == 0,]
  
  avg_send = c()
  std_send = c()
  
  for (date in unique(s$Date)) {
    for (subject in 1:6) {
      avg_send = c(avg_send, mean (s[s$Date == date & s$Subject == subject,]$Contribution))
      std_send = c(std_send, pop.sd (s[s$Date == date & s$Subject == subject,]$Contribution))
    }
  }
  
  std_send = std_send [order (avg_send, decreasing = FALSE)]
  avg_send = sort (avg_send, decreasing = FALSE)
  
  # Plotting average sending and standard deviation of each users
  avg_send = avg_send/10
  std_send = std_send/10
  
  all_avg = c(all_avg, avg_send)
  all_std = c(all_std, std_send)
  
  plot (avg_send, ylab = "Send proportion", xlab = "Player", xlim = c(1,30), ylim = c(-0.5,1.5))
  for (i in 1:30) {
    segments(x0 = i, y0 = avg_send[i] - std_send[i], y1 = avg_send[i] + std_send[i], lty = 2)
    epsilon = 0.1
    segments(x0 = i-epsilon, x1 = i+epsilon, y0 =avg_send[i] - std_send[i], y1=avg_send[i] - std_send[i])
    segments(x0 = i-epsilon, x1 = i+epsilon, y0 =avg_send[i] + std_send[i], y1=avg_send[i] + std_send[i])
  }
  
  # Plotting some fluctuating users
  plot (s[s$Subject == 5 & s$Date == unique(s$Date)[3],]$Contribution, xlab = "Player 17", ylab = "Sending amount", main = "An example of fluctuating user")
  lines (s[s$Subject == 5 & s$Date == unique(s$Date)[3],]$Contribution)
```


```{r echo=FALSE}
  plot (s[s$Subject == 6 & s$Date == unique(s$Date)[3],]$Contribution, xlab = "Player 18", ylab = "Sending amount", main = "An example of fluctuating user")
  lines (s[s$Subject == 6 & s$Date == unique(s$Date)[3],]$Contribution)
```

### Fluctuating with Dubois's data

```{r echo=FALSE}
  dubois <- read.csv("all_data/data_dubois.csv", sep = ";")
  dubois1 <- dubois[1:1080,]
  avg_send = c()
  std_send = c()
  
    for (subject in 1:36) {
      avg_send = c(avg_send, mean (dubois1[dubois1$player_uid == subject,]$sent/10))
      std_send = c(std_send, pop.sd (dubois1[dubois1$player_uid == subject,]$sent/10))
    }
  
  std_send = std_send [order (avg_send, decreasing = FALSE)]
  avg_send = sort (avg_send, decreasing = FALSE)
  
  all_avg = c(all_avg, avg_send)
  all_std = c(all_std, std_send)
  
  plot (avg_send, ylab = "Send proportion", xlab = "Player", xlim = c(1,36), ylim = c(-0.5,1.5))
  for (i in 1:36) {
    segments(x0 = i, y0 = avg_send[i] - std_send[i], y1 = avg_send[i] + std_send[i], lty = 2)
    epsilon = 0.1
    segments(x0 = i-epsilon, x1 = i+epsilon, y0 =avg_send[i] - std_send[i], y1=avg_send[i] - std_send[i])
    segments(x0 = i-epsilon, x1 = i+epsilon, y0 =avg_send[i] + std_send[i], y1=avg_send[i] + std_send[i])
  }
```


### Flucuating with Bravo's data

```{r echo =FALSE}
  bravo <- read.csv (file = "all_data/Data2.csv")
  newID <- unique (bravo$newID)
  
  avg_send = c()
  std_send = c()
  
  for (id in newID) {
    actions <- bravo[bravo$newID == id & !is.na(bravo$daAaB),]$daAaB / 10
    avg_send = c(avg_send, mean (actions))
      std_send = c(std_send, pop.sd (actions))
  }
  
  std_send = std_send [order (avg_send, decreasing = FALSE)]
  avg_send = sort (avg_send, decreasing = FALSE)
  
  all_avg = c(all_avg, avg_send)
  all_std = c(all_std, std_send)
  
  plot (avg_send, ylab = "Send proportion", xlab = "Player", xlim = c(1,108), ylim = c(-0.5,1.5))
  for (i in 1:108) {
    segments(x0 = i, y0 = avg_send[i] - std_send[i], y1 = avg_send[i] + std_send[i], lty = 2)
    epsilon = 0.1
    segments(x0 = i-epsilon, x1 = i+epsilon, y0 =avg_send[i] - std_send[i], y1=avg_send[i] - std_send[i])
    segments(x0 = i-epsilon, x1 = i+epsilon, y0 =avg_send[i] + std_send[i], y1=avg_send[i] + std_send[i])
  }
```

```{r echo=FALSE}
  # The most fluctuate user in Bravo data
  plot (bravo[bravo$newID == 109 & !is.na(bravo$daAaB),]$daAaB / 10, xlab = "Round number", ylab = "Send proportion")
  lines (bravo[bravo$newID == 109 & !is.na(bravo$daAaB),]$daAaB / 10)
```


```{r echo = FALSE}
# Plot all average and std of sending of all 3 datasets in a same plot
  len = length (all_avg)
  plot (all_avg, ylab = "Send proportion", xlab = "Player", xlim = c(1,len), ylim = c(-0.2,1.2))
  for (i in 1:len) {
    segments(x0 = i, y0 = all_avg[i] - all_std[i], y1 = all_avg[i] + all_std[i], lty = 2)
    epsilon = 0.1
    segments(x0 = i-epsilon, x1 = i+epsilon, y0 =all_avg[i] - all_std[i], y1=all_avg[i] - all_std[i])
    segments(x0 = i-epsilon, x1 = i+epsilon, y0 =all_avg[i] + all_std[i], y1=all_avg[i] + all_std[i])
  }
```
## Comparison with other predicting models

### Null model

Null model is the model who predicts that the sending behavior of round n is equal with sending behavior of round (n-1)

```{r echo=FALSE}
null_model = function(ROUND = 8) {
  # Plotting the difference between round N and round N+1
  
  send_round_n_1 = c()
  send_round_n = c()
  
  for (date in unique(s$Date)) {
    for (subject in 1:6) {
      send_round_n_1 = c(send_round_n_1, s[s$Date == date & s$Subject == subject,]$my_send_proportional[ROUND])
      send_round_n = c(send_round_n, s[s$Date == date & s$Subject == subject,]$my_send_proportional[(ROUND + 1)])
    }
  }
  
#   plot (x = send_round_n_1, y = send_round_n, xlab = paste("Sending behavior at round",ROUND), ylab = paste("Sending behavior at round", (ROUND+1)), 
#         main = "Null model")
  
  lm1 = lm (send_round_n ~ send_round_n_1)
  # print (summary (lm1))
  lm1
}
```

We calculate the average R-squared of null model from round 5 to round 10

```{r, echo=FALSE}
  adj_r_squared = c()
  for (round in 4:9) {
    lm1 = null_model (ROUND = round)
    adj_r_squared = c(adj_r_squared, summary(lm1)$adj.r.squared)
  }
  print (paste("Average adj.R.squared of null model:", paste(mean(adj_r_squared))))
```

### Naive model

Naive model is to predict the behavior based on average of previous behavior.

```{r echo=FALSE}
naive_model = function(ROUND = 8) {
  # Plotting the difference between round N and round N+1
  
  send_round_n_1 = c()
  send_round_n = c()
  
  for (date in unique(s$Date)) {
    for (subject in 1:6) {
      send_round_n_1 = c(send_round_n_1, mean (s[s$Date == date & s$Subject == subject,]$my_send_proportional[1:ROUND]))
      send_round_n = c(send_round_n, s[s$Date == date & s$Subject == subject,]$my_send_proportional[(ROUND + 1)])
    }
  }
  
#   plot (x = send_round_n_1, y = send_round_n, xlab = paste("Sending behavior at round",ROUND), ylab = paste("Sending behavior at round", (ROUND+1)), 
#         main = "Naive model")
  
  lm1 = lm (send_round_n ~ send_round_n_1)
  # print (summary (lm1))
  lm1
}
```

```{r, echo=FALSE}
  adj_r_squared = c()
  for (round in 4:9) {
    lm1 = naive_model (ROUND = round)
    adj_r_squared = c(adj_r_squared, summary(lm1)$adj.r.squared)
  }
  print (paste("Average adj.R.squared of naive model:", paste(mean(adj_r_squared))))
```

### Trust function model

```{r echo=FALSE}
my_trust = function (ROUND = 8, data = s) {
  data$my_trust = ave(s$Contribution/10, s$Date, s$Subject, FUN = calcTrust)
  
  last_actions = c()
  last_trusts = c()
  
  for (date in unique(s$Date)) {
    for (subject in 1:6) {
      last_action = data[data$Date == date & data$Subject == subject,]$my_send_proportional[ROUND]
      last_trust = data[data$Date == date & data$Subject == subject,]$my_trust[(ROUND - 1)]
      last_actions = c(last_actions, last_action)
      last_trusts = c(last_trusts, last_trust)
    }
  }
  par (new = FALSE)
  plot (x = last_trusts, y = last_actions, xlab = paste("Trust score before round ", ROUND), ylab = paste("Sending behavior at round ", ROUND),
        cex.lab = 1.5)
  lm2 <- lm(formula = last_actions ~ last_trusts)
  list (last_actions, last_trusts)
  lm2
}
```

```{r, echo=FALSE}
  adj_r_squared = c()
  for (round in 4:9) {
    lm1 = my_trust (ROUND = round)
    adj_r_squared = c(adj_r_squared, summary(lm1)$adj.r.squared)
  }
  print (paste("Average adj.R.squared of our trust model:", paste(mean(adj_r_squared))))
```

### Comparing with Dubois data

```{r echo=FALSE}
  verifyTrustWithDubois <- function (round = 5) {
  dubois <- read.csv("all_data/data_dubois.csv", sep = ";")
  dubois1 <- dubois[1:1080,]
  dubois1$trust <- ave(dubois1$sent/10, dubois1$player_uid, FUN = calcTrust)
  last_trust = dubois1[dubois1$period == (round - 1),]$trust
  last_action = dubois1[dubois1$period == round,]$sent/10
  lm2 <- lm(formula = last_action ~ last_trust)
  summary (lm2)
  }
  
  verifyTrustWithDuboisSimple <- function (round = 5) {
  dubois <- read.csv("all_data/data_dubois.csv", sep = ";")
  dubois1 <- dubois[1:1080,]
  last_trust = c()
  for (uid in unique (dubois1$player_uid)) {
    trust = mean (dubois1[dubois1$player_uid == uid & dubois1$period < round,]$sent/10)
    last_trust = c(last_trust, trust)
  }
  last_action = dubois1[dubois1$period == round,]$sent/10
  lm2 <- lm(formula = last_action ~ last_trust)
  summary (lm2)
  }
  
  verifyTrustWithDuboisNull <- function (round = 5) {
  dubois <- read.csv("all_data/data_dubois.csv", sep = ";")
  dubois1 <- dubois[1:1080,]
  last_trust = c()
  for (uid in unique (dubois1$player_uid)) {
    trust = dubois1[dubois1$player_uid == uid & dubois1$period == (round - 1),]$sent/10
    last_trust = c(last_trust, trust)
  }
  last_action = dubois1[dubois1$period == round,]$sent/10
  lm2 <- lm(formula = last_action ~ last_trust)
  summary (lm2)
  }
```

```{r echo=FALSE}
  sum_r_squared_trust = 0
  sum_r_squared_simple = 0
  sum_r_squared_null = 0
  
  for (round_number in 5:10) {
    sum_r_squared_trust = sum_r_squared_trust + verifyTrustWithDubois (round = round_number)$adj.r.squared
    sum_r_squared_simple = sum_r_squared_simple + verifyTrustWithDuboisSimple (round = round_number)$adj.r.squared
    sum_r_squared_null = sum_r_squared_null + verifyTrustWithDuboisNull (round = round_number)$adj.r.squared
  }
  
  print (paste("Average adj R squared of null model on Dubois data:", sum_r_squared_null/6 ))
  print (paste("Average adj R squared of  simple model on Dubois data:", sum_r_squared_trust/6 ))
  print (paste("Average adj R squared of trust average model on Dubois data:", sum_r_squared_simple/6 ))
  
```

